Flatiron cleaning

### 2021-10-14 Rmd/rdi analysis.Rmd
Update RDI analysis

### How many lines did patients received as Neoadjuvant
`r emo::ji("question_mark")`  
Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.

```{r}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```

@@

`r emo::ji("question_mark")`  
Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
Should we include patients who got a single drug as lot/line? like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>    
`r emo::ji("check")`   
```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
remove_linename_other <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>%

  mutate(remove_linename_other = case_when(
    # keep these drugs in line 1 of upfront chemo and upfront surg
    # linenumber_new == 1 & 
    #   drug_count == 1 &
    #    !str_detect(linename, "platin|taxel")                                 ~ "remove",
    # linenumber_new == 1 &
    #   drug_count == 2 &
    #   (
    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
    #   str_detect(linename, "platin") & str_detect(linename, "Bev") |
    #   str_detect(linename, "taxel") & str_detect(linename, "Bev"))
    #   )                                                                      ~ "remove",
    # linenumber_new == 1 &
    #   drug_count >= 3 &
    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
    # 
    #                                                                          ~ "remove",
    # weird one
    linenumber_new == 1 &
      str_detect(linename, 
                 "parib|bine|Dox|T|F|Clinical|Cyclo|lumab|Tra|ximab|zole|Aza|trex|Gos|lide|Pem")                       
                                                                         ~ "remove",
    linenumber_new == 1 & linename == "Bevacizumab"                      ~ "remove",
    linenumber_new == 2 &
      therapy == "Upfront Chemo" &
      str_detect(linename, 
                 "parib|bine|Dox|T|F|Clinical|Cyclo")                       
                                                                         ~ "remove",
    linenumber_new == 2 &
      therapy == "Upfront Chemo" & linename == "Bevacizumab"             ~ "remove",
    # keep these drugs in line 2 of upfront chemo from when line switch
    # linenumber_new == 2 &
    #   therapy == "Upfront Chemo" &
    #   drug_count == 1 &
    #    !str_detect(linename, "platin|taxel")  ~ "remove",
    #   
    #   
    # linenumber_new == 2 &
    #   therapy == "Upfront Chemo" &
    #   drug_count == 2 &
    #   (
    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
    #   str_detect(linename, "platin") & str_detect(linename, "Bev") |
    #   str_detect(linename, "taxel") & str_detect(linename, "Bev"))
    #   ) ~ "remove",
    #   
    #   
    # linenumber_new == 2 &
    #   therapy == "Upfront Chemo" &
    #   drug_count >= 3 &
    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
    #   # !str_detect(linename, "taxel") &
    #   # !str_detect(linename, "Bev")
    #                     ~ "remove",

    TRUE                                           ~ NA_character_
  )) %>% 
  # group_by(patientid) %>% 
  # fill(remove_linename_other, .direction = "down") %>% 
  # ungroup() %>% 
  arrange(patientid, episodedate) #%>%

@@

# remove_linename_other# <- therapy_line %>% 
  # filter(chemotherapy_type == "Neoadjuvant" &
  #          linenumber_new != 1)
remove_linename_other <- paste(remove_linename_other$patientid, collapse = "|")

# therapy_line %>% 
#   filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
#          ) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
# 
# therapy_line %>% 
#   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))

# therapy_line %>% distinct(patientid) %>% nrow()

therapy_line <- therapy_line %>% 
  # Remove patients with other linename
  filter(!str_detect(patientid, remove_linename_other)) %>% 
  arrange(patientid, episodedate)
# example of keep
```

First table is frontline Neo, second table is frontline Adj.
```{r}
therapy_line %>% 
  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin") %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line and were removed.  
`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin") %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line and were removed.

Patients left:
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
# therapy_line %>% 
#   filter(str_detect(linename, "Car") &
#            drugname == "cisplatin") %>%
#   distinct(patientid) %>% nrow()
# 
# therapy_line %>% 
#   filter(str_detect(linename, "Cisplatin") &
#            drugname == "carboplatin") %>%
#   distinct(patientid) %>% nrow()

remove_switch <- therapy_line %>% 
  filter(
    (str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
  (str_detect(linename, "Cisplatin") & drugname == "carboplatin")
  ) %>%
  distinct(patientid)
remove_switch <- paste(remove_switch$patientid, collapse = "|")

@@

```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
# therapy_line %>% 
#   filter(str_detect(linename, "Pacli") &
#            drugname == "docetaxel") %>%
#   distinct(patientid) %>% nrow()
# therapy_line %>% 
#   filter(str_detect(linename, "Doce") &
#            drugname == "Paclitaxel") %>%
#   distinct(patientid) %>% nrow()
```
`r therapy_line %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel") %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.  
I am removing these patients for now but <span style="color:red">**Do we need to remove the patients that switch from paclitaxel to docetaxel and vice versa since the dosing calculating is the same for both?**</span>

`r emo::ji("question_mark")`

<span style="color:red">**Are you good with thatl?**</span>

Patients left:
```{r}
remove_switch1 <- therapy_line %>% 
  filter(
    str_detect(linename, "Pacli") & drugname == "docetaxel"
  ) %>%
  distinct(patientid)
remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")

@@

`r emo::ji("check")`  
We decided to take the creatine, weight, bsa measured within a month and in the same cycle of the administration.

```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    abs(interval_creat) < 31 &
      creat_date > linestartdate &
      creat_date < lineenddate             ~ interval_creat,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
                        duration(n=1, unit="days"))) %>%
  mutate(interval_weight = case_when(
    abs(interval_weight) < 31 &
      weight_date > linestartdate &
      weight_date < lineenddate             ~ interval_weight,
    TRUE                                    ~ NA_real_
  )) %>% 
  arrange(interval_weight) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
         cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
                          duration(n=1, unit="days"))) %>%
  mutate(interval_bsa = case_when(
    abs(interval_bsa) < 31 &
      bsa_date > linestartdate &
      bsa_date < lineenddate               ~ interval_bsa,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_auc = case_when(
    abs(interval_auc) < 31 &
      auc_date > linestartdate &
      auc_date < lineenddate               ~ interval_auc,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

```{r}
analysis_data <- Treatment
```

### Number of line in treatment and cycle in frontline (more cleaning needs to be done here)
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Don't forget we have that "neo + surg"
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>

# Missingness
Here some representation of missingness in our data:  
- In the first plot (horizontal bar), `r is.na(analysis_data$height_at_dx) %>% sum()` data is missing for height closest to dx but `r analysis_data %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx). Because these parameters overlap only 25 patients will have missing value for all of them.   
- In the second plot (horizontal bar), `r is.na(analysis_data$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(analysis_data$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation). the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
```{r}
library(naniar)
analysis_data %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
  gg_miss_upset()

analysis_data %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
  gg_miss_upset()

# is.na(analysis_data$CrCl) %>% sum()
# is.na(analysis_data$amount) %>% sum()
# is.na(analysis_data$target_auc) %>% sum()

# analysis_data %>% filter(is.na(amount)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
# 
# analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
```
If we remove patients who have at least 1 missing amount administered, we lose `r analysis_data %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.

If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.

# Analysis

<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
```{r Table 1}
analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(vital, raceeth, 
           agecat, "ageatdx",

<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
```{r Table 2}
analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",

<!-- # II.Analysis Treatment -->

<span style="color:green">**Table 3 Summary treatment data by race**</span>

```{r Table 3}
# tbl1 <- 
  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "debulking",
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

# RDI calculation

RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.

@@

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("highly underdose", "underdose", "correct", "perfect", "higher dose", "overdose")))

Frontline <- Frontline %>% 
  filter(str_detect(drugname, "platin|taxel"))
```

# Analysis

## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

>>>>

@@

Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>    
`r emo::ji("check")`   
```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
remove_linename_other <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>%

  mutate(remove_linename_other = case_when(
    linenumber_new == 1 &
      str_detect(linename, 
                 "parib|bine|Dox|T|F|Clinical|Cyclo|lumab|Tra|ximab|zole|Aza|trex|Gos|lide|Pem")                       
                                                                         ~ "remove",
    linenumber_new == 1 & linename == "Bevacizumab"                      ~ "remove",
    linenumber_new == 2 &
      therapy == "Upfront Chemo" &
      str_detect(linename, 
                 "parib|bine|Dox|T|F|Clinical|Cyclo")                       
                                                                         ~ "remove",
    linenumber_new == 2 &
      therapy == "Upfront Chemo" & linename == "Bevacizumab"             ~ "remove",
    TRUE                                           ~ NA_character_
  )) %>% 
  arrange(patientid, episodedate)

@@

remove_linename_other <- paste(remove_linename_other$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # Remove patients with other linename
  filter(!str_detect(patientid, remove_linename_other)) %>% 
  arrange(patientid, episodedate)
```

First table is frontline Neo, second table is frontline Adj.
```{r}
therapy_line %>% 
  filter(linenumber == 1
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line and were removed.  
`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line and were removed.

Patients left:
```{r}
# switch cispl vs carbo  Car > Cis F1BF7208F0E96

remove_switch <- therapy_line %>% 
  filter(linenumber_adj == 1 &
    ((str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
  (str_detect(linename, "Cisplatin") & drugname == "carboplatin"))
  ) %>%
  distinct(patientid)
remove_switch <- paste(remove_switch$patientid, collapse = "|")

@@

`r therapy_line %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.  
I am removing these patients

Patients left:
```{r}
remove_switch1 <- therapy_line %>% 
  filter(
    str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1
  ) %>%
  distinct(patientid)
remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")

@@

`r emo::ji("check")`  
We decided to take the creatinine, weight, bsa measured within a month and in the same cycle of the administration AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line

```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    (therapy == "Upfront Surgery" &
       interval_creat < 31 &
       creat_date < lineenddate &
       creat_date > surgerydate)                  ~ interval_creat,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_creat < 31 &
           creat_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_creat < 31 &
             creat_date < lineenddate &
             creat_date > surgerydate)
      )                                          ~ interval_creat,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
                        duration(n=1, unit="days"))) %>%
  mutate(interval_weight = case_when(
    (therapy == "Upfront Surgery" &
       interval_weight < 31 &
       weight_date < lineenddate &
       weight_date > surgerydate)                  ~ interval_weight,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_weight < 31 &
           weight_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_weight < 31 &
             weight_date < lineenddate &
             weight_date > surgerydate)
      )                                          ~ interval_weight,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_weight) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
         cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
                          duration(n=1, unit="days"))) %>%
  mutate(interval_bsa = case_when(
    (therapy == "Upfront Surgery" &
       interval_bsa < 31 &
       bsa_date < lineenddate &
       bsa_date > surgerydate)                  ~ interval_bsa,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_bsa < 31 &
           bsa_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_bsa < 31 &
             bsa_date < lineenddate &
             bsa_date > surgerydate)
      )                                          ~ interval_bsa,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_auc = case_when(
    (therapy == "Upfront Surgery" &
       interval_auc < 31 &
       auc_date < lineenddate &
       auc_date > surgerydate)                  ~ interval_auc,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_auc < 31 &
           auc_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_auc < 31 &
             auc_date < lineenddate &
             auc_date > surgerydate)
      )                                          ~ interval_auc,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

@@

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("correct", "highly underdose", "underdose", "perfect", "higher dose", "overdose")))

Frontline <- Frontline %>% 
  filter(str_detect(drugname, "platin|taxel"))
```
<br>
<br>
<br>

### Number of line in treatment and cycle in frontline (more cleaning needs to be done here)
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Don't forget we have that "neo + surg"
```{r}
Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

Frontline %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
Frontline %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Frontline %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
Frontline %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Frontline %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>
